Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-01-06 paper.tex
change figure6 and text

\bjoern{STOP}{HERE}

>>>>

\bjoern{STOP}{HERE}
The analytical forms of the distribution $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, $P_J(\log_{10}(\tau))$ and $P_\mathbf{x}(\log_{10}(\tau))$ are usually unknown. 
To quantify the uncertainty and variability in the sample data, we calculate a $99\%$ confidence interval around the median. 
This statistical quantity is typically nonparametric, and relies on percentiles of the data, making it robust to different types of probability mass function.

Using the equal-tailed percentile method, its calculation involves sorting the data and determining percentiles that correspond to the desired confidence level.
Given a dataset $\{ \tau_1, \tau_2, \dots, \tau_n \}$, the procedure can be described as follows:
\begin{enumerate}
  \item Sort the data in ascending order. For a confidence level $CL$, the corresponding complement 
  $1-CL$ determines the tails of the interval. 
  \item Find the lower bound $\tau_{\eta}$ corresponds to the $\eta$-th percentile of the dataset where $\eta = (1-CL)/2$. For a $99\%$ confidence interval, $\eta=0.05$.
  \item Find the upper bound $\tau_{(1-\eta)}$ corresponds to the $(1-\eta)$-th percentile of the dataset.
  \item The confidence interval around the median is $[\tau_{\eta}, \tau_{(1-\eta)}]$.
\end{enumerate}
